\graphicspath{ {images/} }
\chapter{Analysis}
%\subsection*{}
%\textbf{[1]}\\
\hspace{5mm} In this chapter you need to  List all methods which suits to your proposed system. And then select most appropriate method for your project by doing feasibility study.
Some comparative study will help to select one out of other appropriate methods.

\section{Any Type of Analysis} 
List to list all methodologies that you found during literature survey. Explain all algorithms that will be use in your project.

\hspace{5mm}In this section all algorithms or any other implementation procedure need to explain with proper flow.
\par describe every procedure or algorithm with necessary diagram.
\par also explain different technology or languages you used for implementation/Deployment.


\section{Software project analysis}
Ok, lets assume you have specification now. As a next level, you will want to know, how big the project really is, how much time it will take to implement it, what will be the costs and if all your requirements can be met.

To able to answer such questions, the analysis of all requirements and possible problems is needed. If the project is very complex, it may need splitting into smaller sub-projects ("divide and rule"). For each phase of the project, the need resources (people, time, money, tools, technologies) need to be identified and calculated.

The output of this phase is a written analysis document, which includes at least:

\begin{itemize}
    \item detailed system description
    \item detailed system description
    \item identification of project phases
    \item resource estimation
    \item time schedule
    \item identification of possible problems known at this stage and suggestion how to prevent them
    \item list and recommendations of technologies to be used
\end{itemize}
