\begin{thebibliography}{References}
\addcontentsline{toc}{chapter}{References}
%---------------------------------------------------------
\bibitem{chop}
Chopda, J., Raveshiya, H., Nakum, S. and Nakrani, V., Cotton Crop Disease Detection using Decision Tree Classifier, \textit{International Conference on Smart City and Emerging Technology (ICSCET)},\hskip 1em plus 0.5em minus 0.4em\relax IEEE, pp. 1-5, January 2018.
%------------------------------------------------------------------------
\bibitem{kamb}
Kamble, J.K., Plant Disease Detector, \emph{International Conference on Advances in Communication and Computing Technology (ICACCT)},\hskip 1em plus 0.5em minus 0.4em\relax pp. 97-101, February 2012.
%------------------------------------------------------------------------
\bibitem{kul}
Kulkarni, O., Crop Disease Detection Using Deep Learning, \emph{Proceedings of Journal of Global Research in Computer Science
},\hskip 1em plus 0.5em minus 0.4em\relax Volume 4, No.4, April 2013.
%------------------------------------------------------------------------
\bibitem{miq}
Mique Jr, E.L. and Palaoag, T.D., Rice Pest and Disease Detection Using Convolutional Neural Network, \emph{International Conference on Information Science and System},\hskip 1em plus 0.5em minus 0.4em\relax ACM, pp. 147-151, April 2018.
%------------------------------------------------------------------------
\bibitem{pado}
Padol, P.B. and Yadav, A.A., SVM classifier based grape leaf disease detection, \emph{Conference on advances in signal processing (CASP)},\hskip 1em plus 0.5em minus 0.4em\relax IEEE, pp. 175-179, June 2016.
%------------------------------------------------------------------------
\bibitem{petr}
Petrellis, N., Mobile Application for Plant Disease Classification Based on Symptom Signatures, \emph{21st Pan-Hellenic Conference on Informatics},\hskip 1em plus 0.5em minus 0.4em\relax ACM, p. 1, September 2017.
%------------------------------------------------------------------------
\bibitem{zeng}
Zeng, W., Li, M., Zhang, J., Chen, L., Fang, S. and Wang, J., High-Order Residual Convolutional Neural Network for Robust Crop Disease Recognition,\textit{2nd International Conference on Computer Science and Application Engineering},\hskip 1em plus 0.5em minus 0.4em\relax ACM, p. 101, October 2018. 
%------------------------------------------------------------------------
\bibitem{singh}
Singh, V. and Misra, A.K., 2015, March. Detection of unhealthy region of plant leaves using image processing and genetic algorithm, \emph{International Conference on Advances in Computer Engineering and Applications},\hskip 1em plus 0.5em minus 0.4em\relax IEEE, pp. 1028-1032, March 2015.
%------------------------------------------------------------------------
\bibitem{sard}
Sardogan, M., Tuncer, A. and Ozen, Y., 2018, September. Plant leaf disease detection and classification based on CNN with LVQ algorithm, \emph{3rd International Conference on Computer Science and Engineering (UBMK)},\hskip 1em plus 0.5em minus 0.4em \relax IEEE, pp. 382-385, September 2018.
%------------------------------------------------------------------------

\end{thebibliography}

