\begin{thebibliography}{References}
\addcontentsline{toc}{chapter}{References}
%---------------------------------------------------------
\bibitem{aless}
Alessandro Armando, Gabriele Costa, Alessio Merlo, Bring Your Own Device, Securely, \textit{Proceedings of the 28th Annual ACM Symposium on Applied Computing},\hskip 1em plus 0.5em minus 0.4em\relax ACM New York, NY, USA , pp. 1852-1858 March 2013.
%------------------------------------------------------------------------
\bibitem{ben}
Rebecca Copeland, Noel Crespi, Analyzing Consumerization - Should Enterprise Business Context Determine Session Policy?, 2012 IEEE\emph{Proceedings of 16th International Conference on Intelligence in Next Generation Networks (ICIN)},\hskip 1em plus 0.5em minus 0.4em\relax pp.187-193 ,2012.
%------------------------------------------------------------------------
\bibitem{pra}
Prashant Kumar Gajar, Arnab Ghosh, Shashikant Rai,BRING YOUR OWN DEVICE (BYOD): SECURITY RISKS AND MITIGATING STRATEGIES\emph{Proceedings of Journal of Global Research in Computer Science
},\hskip 1em plus 0.5em minus 0.4em\relax Volume 4, No.4, April 2013.
%------------------------------------------------------------------------
\bibitem{sean}
Sean Chung, Sam Chung, Teresa Escrig, Yan Bai,Barbara Endicott-Popovsky,2TAC: Distributed Access Control Architecture for “Bring Your Own Device” Security
,' \emph{proceeding of the International Conference on BioMedical Computing},\hskip 1em plus 0.5em minus 0.4em\relax2012.
%------------------------------------------------------------------------
\bibitem{dennis}
Dennis Titze, Philipp Stephanow, Julian Schutte,'A Configurable and Extensible Security Service Architecture for Smartphones,' \emph{IEEE Transactions on 27th International Conference on Advanced Information Networking and Applications Workshops},\hskip 1em plus 0.5em minus 0.4em\relax 2013.
%------------------------------------------------------------------------
\bibitem{dae}
Dae Hyeob Kim, Ji Hoon Gong, Won Hyung Park, Neo Park, `Vulnerability of Information Disclosure in Data
Transfer Section for Safe Smartwork Infrasturucture',\textit{IEEE transaction on International Conference on Information Science and Applications (ICISA), 2013 }, pp. 1 - 3, 24-26 June 2013. 
%------------------------------------------------------------------------
\bibitem{den}
Dennis Gessner, Joao Girao, Ghassan Karame, Wenting Li
'Towards a User-Friendly Security-Enhancing BYOD Solution'\emph{Proceedings of the NEC technical journal},\hskip 1em plus 0.5em minus 0.4em\relax Vol.7 No.3/2013.
%------------------------------------------------------------------------
\bibitem{hanay}
Hanay, Y.S. , Wolf, T.,'Techniques for Policy Enforcement on Encrypted Network Traffic', \textit{Proceedings of the Military Communications Conference, 2009. MILCOM 2009. IEEE },\hskip 1em plus 0.5em minus 0.4em\relax  PP. 1-7,2009. 
%------------------------------------------------------------------------
\bibitem{annis}
Ioannis Koskosas,`A Short Literature Review in Information Systems Security Approaches,' \emph{Proceeding of the IJAKECS},\hskip 1em plus 0.5em minus 0.4em\relax Vol.1 No.1,pp.1-7, January- June 2013.
%------------------------------------------------------------------------
\bibitem{ant}
Antonio Scarfò, 'New security perspectives around BYOD'
\emph{IEEE Transactions Seventh International Conference on Broadband, Wireless Computing, Communication and Applications},\hskip 1em plus 0.5em minus 0.4em\relax Page(s): 446-451,2012
%------------------------------------------------------------------------
\bibitem{apex}
Mohammad Nauman, Sohail Khan, Xinwen Zhang,'Apex: Extending Android Permission Model and
Enforcement with User-deﬁned Runtime Constraints',
\emph{ASIACCS '10 Proceedings of the 5th ACM Symposium on Information, Computer and Communications Security},\hskip 1em plus 0.5em minus 0.4em\relax Pages 328-332,2010
%------------------------------------------------------------------------------
\bibitem{andro}
Ionut Andronache, Claudiu Nisipasiu,'Web Single Sign-On Implementation SimpleSAMLphp Application',
\emph{Journal of Mobile, Embedded and Distributed Systems},\hskip 1em plus 0.5em minus 0.4em\relax vol. III, no. 1, 2011
%------------------------------------------------------------------------------
\end{thebibliography}

